An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-11-28 jmiv.tex
correction of equation 5 development in section 4.1

We define $O_{r}^{(i)}(y) := O^{(i)} \cap B_r(y)$ and an analogous definition holds for $F_{r}^{(i)}(y)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
\begin{align*}
  \hat{\kappa}^2(y) &= c_1\Big( c_2 - \sum_{x_j \in B_r(y)} \big( {x_j} + |F_{r}^{(i)}(y)| \big) \Big)^2 \\
   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
\end{align*}
where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. By ignoring constants and multiplication factors and using
the binary character of the variables, we define the following family
of energies for given parameters $\alpha,\beta, \gamma \geq 0$.
\begin{align}
  E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
  & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
  & + \sum_{x \in X}{\gamma g(S,x)},
  \label{eq:energy-family}
\end{align}
where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term. Each choice of $m$ generates a different flow, which is generally described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.

>>>>

We define $O_{r}^{(i)}(y) := O^{(i)} \cap B_r(y)$ and an analogous definition holds for $F_{r}^{(i)}(y)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
\begin{align*}
  \hat{\kappa}^2(y) &= c_1\Big( c_2 - |F_{r}^{(i)}(y)| - \sum_{x_j \in O_r^{(i)}(y)} \big( {x_j}  \big) \Big)^2 \\
   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
\end{align*}
where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. By ignoring constants and multiplication factors and using
the binary character of the variables, we define the following family
of energies for given parameters $\alpha,\beta, \gamma \geq 0$.
\begin{align}
  E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
  & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
  & + \sum_{x \in X}{\gamma g(S,x)},
  \label{eq:energy-family}
\end{align}
where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term. Each choice of $m$ generates a different flow, which is generally described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
